HTLSDstack

### 2025-06-14 Code/R/Research/HTLSDstack.Rmd
Dstack recovery rmse by L

>>>>

```{r}
plot_name <- "real_rec_rmse"
load(file = paste0("./Research/comp_results/htlsd_byL_", plot_name, ".RData"))
methods_names <- list(ssa = "SSA", SSADstack = "SSADstack", 
                      tens1 = "Tensor, r3 = 4")
extreme_rmse <- rmse_df |>  pivot_longer(cols = ssa:tens1,
                                         names_to = "Method",
                                         values_to = "RMSE") |>
  group_by(sd, Method) |> summarize(min = min(RMSE), max = max(RMSE))

for (sd_k in sds[sds != 0]) {
  ext_rmse_oth <- filter(extreme_rmse, sd == sd_k, Method != "ssa")
  ext_rmse_esprit <- filter(extreme_rmse, sd == sd_k, Method == "ssa")
  p1 <- rmse_df |> filter(sd == sd_k) |>
    pivot_longer(cols = ssa:tens1,
                 names_to = "Method",
                 values_to = "RMSE") |>
    filter(Method == "ssa") |>
    ggplot(aes(x = Ls_ssa, y = RMSE)) +
    geom_line() +
    geom_hline(
      yintercept = min(ext_rmse_oth$min),
      linetype = 2,
      color = "gray20"
    ) +
    annotate(
      "label",
      x = (Ls_ssa[Ls_len] + Ls_ssa[1]) * 0.38,
      y = min(ext_rmse_oth$min) * 0.95,
      label = paste0("Minimum for other methods\n(achieved on ", methods_names[[ext_rmse_oth$Method[which.min(ext_rmse_oth$min)]]], ")")
    ) +
    ggtitle(paste0("SSA, sd = ", sd_k)) +
    theme_minimal() +
    xlab("L")

  p2 <- rmse_df |> filter(sd == sd_k) |>
    pivot_longer(cols = ssa:tens1,
                 names_to = "Method",
                 values_to = "RMSE") |>
    filter(Method != "ssa") |>
    ggplot(aes(x = Ls_dstack, y = RMSE)) +
    geom_line(aes(col = Method, lty = Method)) +
    geom_hline(
      yintercept = min(ext_rmse_esprit$min),
      linetype = 2,
      color = "gray20"
    ) +
    annotate(
      "label",
      x = (Ls_dstack[Ls_len] + Ls_dstack[1]) * 0.38,
      y = min(ext_rmse_esprit$min) * 1.01,
      label = paste0("Minimum for SSA")
    ) +
    scale_linetype_discrete(labels = c("SSADstack", "Tensor, r3 = 4")) +
    scale_color_discrete(labels = c("SSADstack", "Tensor, r3 = 4")) +
    ggtitle(paste0("Dstack methods, sd = ", sd_k)) +
    theme_minimal() +
    xlab("L")
  pdf(paste0("./img/htlsd_byL_", plot_name, "_ssa_", which(sds == sd_k), ".pdf"),
      width = 9,
      height = 7)
    print(p1)
  dev.off()
  pdf(paste0("./img/htlsd_byL_", plot_name, "_dstack_", which(sds == sd_k), ".pdf"),
      width = 9,
      height = 7)
    print(p2)
  dev.off()
  print(p1)
  print(p2)
}
```
